\documentclass[margin,line,a4paper]{resume}

\usepackage[latin1]{inputenc}
\usepackage[english,danish]{babel}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{url}

\usepackage[colorlinks=true, a4paper=true, pdfstartview=FitV,
linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}

\begin{document}
    {\sc \Large Curriculum Vitae -- Yaseen Hamdulay}
    \begin{resume}
        \vspace{0.5cm}

        \section{\mysidestyle Personal Information}
            Yaseen Hamdulay\\
            19 Civic Rd\\ %fairly certain that they don't care where I stay
            Kenwyn\\
            Cape Town\\
            South Africa\\
            \\
            Tel: +27 76 945 9577\\
            Email: \href{mailto:yaseen@hamdulay.co.za}{yaseen@hamdulay.co.za}\\
            Website: \href{http://hamdulay.co.za}{http://hamdulay.co.za}\\
            GitHub: \href{http://github.com/MrHamdulay}{http://github.com/MrHamdulay}\\

        \section{\mysidestyle Work Experiences}
            \begin{description}
                \item[2go Interactive] (2012 - 2013 December vacation) \\
                    2go is the biggest mobile social network in Nigeria. I worked on the Friendura app for Android. 
                    This was very challenging due to the massive scope. The biggest lesson I took away from 
                    2go was the importance of designing before starting on a project. I was burnt by this 
                    mistake and had this nailed into me constantly.

                \item[SnapBill] (2011 December vacation - mid 2012) \\
                    I started at SnapBill as a December vacation intern working on a number of SnapBill 
                    sub-systems. At the end of my internship I was offered a part-time position while studying 
                    cat UCT. Because SnapBill had such a small development team I had to learn the entire stack 
                    used by SnapBill. I learned how to use many interesting tools and products like node.js, 
                    Redis, Puppet and Continuous Integration systems. Besides learning interesting technologies 
                    I also had to consider the entire application lifecycle. 

                \item[New Media Labs] (2011) \\
                    At New Media Labs I was one of four interns working on porting their WeLove iPhone app to Android.
                    I was exposed to Agile methodologies for the first time at New Media Labs and learnt a lot about
                    working together as a team.

                \item[Tellumat] (2009) \\
                    Mostly job shadowing but I helped debug some of their logging support systems
                in Matlab.

                \item[MXit Lifestyle Ltd] (2008) \\
                    In 2009 I was a finalist (top four) in the MXit PC Client development competition. The winning 
                    prize was R100 000 and I think I did fairly well for a high school student with no formal 
                    programming education. A few months later I was invited to intern at MXit over the school 
                    holidays. At MXit I was exposed to Enterprise level systems for the first time.
            \end{description}

        \section{\mysidestyle Education}
            \begin{description}
                \item[University of Cape Town] (2012 - present) \\
                    Second year BSc majoring in Computer Science and Computer Engineering. \\
                    Achieved Dean's list in first year.
                \item[Wynberg Boys High School] (2007 - 2011)
                \item[Golden Grove Primary School] (2000 - 2006)
            \end{description}

        \section{\mysidestyle Computer Skills}
            \begin{description}
                \item [Operating Systems] Experienced in using Unix systems.

                \item [Programming, Scripting and Markup Languages] Python, C++ / C, Java, PHP, HTML and JavaScript.

                \item [Other technologies] Android, MySQL, Twisted, Flask and Amazon Web Services
            \end{description}

        \section{\mysidestyle Competitions}
            \begin{description}
                \item [International Collegiate Programming Contest (South Africa)] Placed second out of all South African teams.
                \item [Standard Bank IT Challenge] (2012) Won R150 000 for UCT and laptops for myself and the rest of the team.
                \item [Stripe] (2012) Successfully complete the Stripe (a credit card processing company in the USA) CTF challenge. 
                    It's a web security challenge that requires you to find vulnerabilities in a given web app.

                \item [South African Computer Olympiad] (2011) Bronze medalist with Python prize.

                \item [International Olympiad in Informatics] (Thailand, 2011) An individual 
                algorithms based competition for High School students. One of four selected
                to represent South Africa.

                \item [Standard Bank IT Challenge] (2011, 2010) Entered as part of an unofficial team
                as we didn't fit the entry requirements (we needed to be part of a university).
                We came first, beating all the University teams in the process.

                \item [South African Computer Olympiad] (2010) Made it through to the 3rd
                round (top 16).

                \item [MXit programming competition] (2008) Programming competition where we
                had to design a new and innovative MXit client.  Some of the
                entries were from IT professionals. Despite the tough competition I made it to the top 5.
            \end{description}

        \section{\mysidestyle Other Interests}
            \begin{description}
                \item[Capoeira] is an Afro-Brazillian art combining Dance, Martial Arts and Music. It has
                    been a large part of my life for over a year. I have completed my first Batizado.
                \item[Guitar]
                \item[Rock Climbing]
            \end{description}

        \section{\mysidestyle Societies}
            \begin{description}
                \item [UCT Capoeira] Treasurer (2013)
                \item [UCT Algorithm Circle] A society run by UCT students where we learn about and
                each other problem solving methods and skills.

                \item [Project Umonya] A project that aims to promote computer science and programming
                to South African learners. We have weekend long courses to interested high school students
                in the hope that it will spark an interest in programming. I'm one of the tutors at the course.
            \end{description}

        \section{\mysidestyle References}
            Available on request
    \end{resume}
\end{document}
